Intentional stocking undermines ecological stability

### 2022-03-04 rmd/manuscript.Rmd
Update manuscript.Rmd

The past decades have witnessed efforts to unveil ecological risks associated with massive releases of captive-bred individuals ("stock enhancement") [@arakiHatcheryStockingHelp2010; @krkosekDecliningWildSalmon2007]. Yet, this method is still pervasive in conservation and natural resource management, assuming that the demographic benefits exceed the associated risks [@kitadaEconomicEcologicalGenetic2018; @laikreCompromisingGeneticDiversity2010]. Here, contrary to this intuition, we show that stock enhancement triggers community collapse with little demographic benefit to the enhanced species. Our theory predicted that stock enhancement destabilizes community dynamics by facilitating competitive exclusion. In parallel, the excessive input of captive-bred individuals suppressed the natural recruitment of the enhanced species via intensified within-species competition. Consistent with this prediction, stream fish communities showed greater temporal fluctuations and fewer species richness in rivers with the intensive stocking of hatchery masu salmon - a major freshwater resource in Japan [@kitadaLessonsJapanMarine2020]. The current overreliance on stock enhancement may accelerate global biodiversity loss, threatening the provisioning of ecosystem services. A radical change in management strategies is therefore required for the sustainability of natural resources.

>>>>

The past decades have witnessed efforts to unveil ecological risks associated with massive releases of captive-bred individuals ("stock enhancement") [@arakiHatcheryStockingHelp2010; @krkosekDecliningWildSalmon2007]. Yet, this method is still pervasive in conservation and natural resource management, assuming that the demographic benefits exceed the associated risks [@kitadaEconomicEcologicalGenetic2018; @laikreCompromisingGeneticDiversity2010]. Here, contrary to this intuition, we show that stock enhancement triggers community collapse with little demographic benefit to the enhanced species. Our theory predicted that stock enhancement destabilizes community dynamics by facilitating competitive exclusion. In parallel, the excessive input of captive-bred individuals suppressed the natural recruitment of the enhanced species via intensified within-species competition. Consistent with this prediction, stream fish communities showed greater temporal fluctuations and fewer species richness in rivers with the intensive stocking of hatchery masu salmon - a major freshwater resource in Japan [@kitadaLessonsJapanMarine2020]. Our findings alarm that the current overreliance on stock enhancement may accelerate global biodiversity loss, threatening the provisioning of ecosystem services. A radical change in management strategies is therefore required for the sustainability of natural resources.
